Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-08-19 paper/spectraldensity.tex
correct typo in bibliography key

The pseudoinverses on \reflin{lin:4-nystromchebyshev-nystrom-pp} need to be computed with care. It is possible to reformulate the problem as a generalized eigenvalue problem and apply thresholding to the smallest eigenvalues of a certain matrix to enforce stability \cite{lin-2017-randomized-estimation, epperly-2022-theory-quantuma}. Since this renders the algorithm significantly more complicated but only improved the accuracy slightly during our experiments, we will instead evaluate these expressions in \reflin{lin:4-nystromchebyshev-nystrom-pp} using a least-squares solver which likewise uses a truncation of the smallest eigenvalues to enforce better conditioning.

>>>>

The pseudoinverses on \reflin{lin:4-nystromchebyshev-nystrom-pp} need to be computed with care. It is possible to reformulate the problem as a generalized eigenvalue problem and apply thresholding to the smallest eigenvalues of a certain matrix to enforce stability \cite{lin-2017-randomized-estimation, epperly-2022-theory-quantum}. Since this renders the algorithm significantly more complicated but only improved the accuracy slightly during our experiments, we will instead evaluate these expressions in \reflin{lin:4-nystromchebyshev-nystrom-pp} using a least-squares solver which likewise uses a truncation of the smallest eigenvalues to enforce better conditioning.
